Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-03-23 main.Rmd
figure 7 caption

```{r bothcust, fig.cap = "(a) Area quantile and (b) violin plot and (c) box plot of energy consumption for customer id: 10017936. Plot (a) helps to compare different hours of the day within weekdays and weekends. Plot (b) shows early morning hours are bimodal implying both high and low consumptions are probable due to different seasons. Plot (c) shows the effect of change in mapping which leads to easier comparison between weekdays and weekends for each hour.", out.width="90%"}

>>>>

```{r bothcust, fig.cap = "Energy consumption of a single customer shown with different distribution displays, and granularity arrangements. Two granularities are used: hour of the day (I) and  weekday/weekend (II). Plot (a) shows granularity I facetted by granularity II, and plots (b), (c) shows the converse mapping. Plot (a) makes a comparison of usage by workday within each hour of the day using side-by-side boxplots. Generally, on a work day there is more consumption early in the day.  Plots (b) and (c) examine the temporal trend of consumption over the course of a day, separately for the type of day. Plot (b) uses an area quantile to put the emphasis on the time series, for example, the median consumption over time shows prolonged usage in the morning on weekdays. Plot (c) uses a violin plot to place emphasis on distributional differences across hours. It can be seen that the morning use on weekdays is bimodal, some work days there is low usage, which might indicate the person is working from home and also having a late start. (FIXME: make nice axis labels)", out.width="90%"}
